What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-09 lda-paper.tex
submitted to migod and ric

@@

@@

>>>>

The query optimizer was a topic which recurred multiple times during
MaxDB's development. In our plots, topics which mention optimizer
occur four times yet in the large static plot (Figure
\ref{fig:statictopics}) it is not in any of the topics. A query
optimizer is rather important to an DBMS, but as we've shown it just
doesn't pop up as a topic on its own. We tried to remove words to see
if we could get optimizer topic out, after removing stop words and
then two of the most common words the global analysis finally had a
topic with optimizer in its topic ten words. This shows that optimizer
was important but it had been obscured, while it would have been
noticed using a more locally relevant approach that we propose.

@@

XXX Numbers and more argument

@@

% Even with our liberal topic similarity metrics that produced both
% long and short trends, we showed that there are only a few trends in a
% repository which recur. Since so few trends recur and so many
% trends appear only once this suggests that global topic analysis might
% be ignoring locally unique topics.

% The utility of global topic analysis is questionable if the value of
% information decreases as it becomes older. Perhaps older trends will
% dominate the topic analysis. Windowed localized topic analysis show
% what are the unique topics.

XXX summarize our position

XXX Add more detail here
